### 2015-03-12 report/report.tex
latest version

\documentclass[3p,number,sort&compress,times]{elsarticle}
\usepackage{amsmath,amsfonts}  %for mathstyles
\usepackage{hyperref}
\usepackage{color}
%\usepackage{colortbl}
\usepackage{wasysym}
%\usepackage{ifsym}
\usepackage{array}
\usepackage{longtable}
\usepackage{graphicx}
\journal{..}
%opening

\begin{document}
\begin{frontmatter}
%\preprint{}
\title{Optimal strategies of influence in structured populations}
\author[ex]{Colin J. Torney}
\author[eeb]{Simon A. Levin}
%
%\cortext[cor1]{Corresponding author}
\address[ex]{Centre for Mathematics \& the Environment, University of Exeter, Penryn Campus, Cornwall, UK}
\address[eeb]{Department of Ecology \& Evolutionary Biology, Princeton University, Princeton, NJ, USA}

\begin{abstract}
Conventions, opinions, or social norms often persist within interacting populations long after their usefulness has ended or their inaccuracy revealed. In many scenarios this is due to conformity by individuals, or the devaluation of individual preferences and opinions when they contradict observed social information. Both the behavior at the individual-level and the structure of the social network play a role in transitions away from out-dated, collectively-held opinions. Personal preferences, biases and the predilection to conform are significant factors, however system level characteristics, such as the statistical properties of the network, or the rate of social mixing, are also strong determinants of macroscale behavior. When seeking to influence a collective decision, different strategies may be more or less effective depending on these factors. Here we show that the effectiveness of a given strategy of influence is dependent on the nature of the underlying interaction network. 
\end{abstract}

\end{frontmatter}

We assume a binary decision process in which individuals make use of social and personal information. Personal information is described by an estimate of a global information source $G\in(1,-1)$. The estimate made by individual $i$, denoted $g_i$, is defined as a random variable drawn from a Laplace distribution, centered on the correct option,
\begin{equation}
P(g_i) = \frac{1}{2\sigma} \exp{ \left( - \frac{\vert g_i - G \vert}{\sigma} \right)}
\end{equation}
(This distribution is chosen for analytical tractability, but equivalent results may be attained for other symmetric distributions, e.g. Gaussian.)

Each individual, $i$, holds an opinion $S_i \in \{ -1,1\}$ that is observable by others in its local neighborhood and is correct when $S_i = \mbox{sign}(G)$. Individuals update their states based on social and personal information and a Bayesian decision rule \cite{nitzan1982optimal,perez2011collective, Perreault, torney2015} is employed. This means that an individual will switch to the state that is the most likely to be correct, given all available information. Formally, individual $i$ will adopt the state $S_i=1$ if
\begin{equation}
 P\left(G \ge 0\big| g_i, \mathbf{S}_{j\in \mathcal{N}_i}\right)  > P\left(G < 0\big| g_i, \mathbf{S}_{j\in \mathcal{N}_i}\right)
\label{opt_sol1}
\end{equation}
where $\mathcal{N}_i$ defines the social interaction neighborhood. To impose a decision rule as a function of $g_i$ we rearrange Eqn.~\ref{opt_sol1} using Bayes' rule, assume individuals place equal weighting on the opinions of neighbors, that they know the level of noise in the environmental cue, and that it is symmetric around zero. Eqn.~\ref{opt_sol1} may then be written as,
\begin{equation}
\frac{\exp{ \left( - \frac{\vert g_i -  \infty \vert}{\sigma} \right)}}{\exp{ \left( - \frac{\vert g_i + \infty \vert}{\sigma} \right)}} > \chi^{1-2x_L}.
\label{rule}
\end{equation}
Here we have denoted the fraction of neighbors an individual observes in the state $S=1$ as $x_L$, used $\pm \infty$ as estimates of the actual value of $G$ (these will cancel), and introduced a social weighting variable $\chi$ which may be interpreted as the belief that a single neighbor is correct rescaled by the neighborhood size. This rescaling means decisions are based on the fraction of neighbors that are correct in the local neighborhood and not the absolute number, ensuring a comparison can be made between social networks with varying average degree.

Rearranging Eqn.~\ref{rule} leads to a decision rule such that individual $i$ will adopt the opinion $S_i = 1$ iff
\begin{equation}
g_i >  \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
\label{opt_rule}
\end{equation}

%, i.e. $\chi = P(S_j=\mbox{sign}(G))^{\vert \mathcal{N}_i \vert }$  the and denote the fraction of neighbors an individual observes in the state $S=1$ as $x_L$. Then the decision rule for the focal individual is to switch to the state $1$ if

We simulate the model and investigate how influencing the system by altering $\sigma$ is impacted by the size and structure of the interaction network. We begin by assuming all individuals are in the incorrect state, i.e. $S=-1$ and $G=1$, and examine the time to escape this state, denoted $\tau$. Key variables are the transitivity and degree of the social network.

We aim to assess optimal strategies assuming some cost associated with reducing the noise. Cost is per unit time and assumed to scale exponentially so that forcing $\sigma \rightarrow 0$ incurs exponentially increasing costs,
\begin{equation}
\mbox{Cost} = \tau (\sigma) e^{\beta N/\sigma}
\label{cost}
\end{equation}
Minimizing Eqn.~\ref{cost} means the optimal level of $\sigma$ is one for which
\begin{equation}
N^{-1} \frac{d \ln \tau}{d \sigma} = \beta \sigma^{-2}
\end{equation}
\begin{figure*}
\centering
\includegraphics[scale=0.4]{figures/fig-chi.eps} 
\caption{Probability to transition as a function of local neighbourhood for different values of the sociality weighting $\chi$}
\label{fig1}
\end{figure*}
We need to find $\tau$.
\section{Mean first passage time away from incorrect state}
Consider the process as a one-step Markov chain on the integer line from $0$ to $N$. A transition from state $j$ to $j+1$ is written $t^+(j)$ and an opposite transition is denoted $t^-(j)$. An exact expression for the mean first passage time from zero individuals correct to $N_{ESC}$ is \cite{gardiner}

\begin{equation}
\tau = \sum\limits_{m=0}^{N_{ESC}} \left( \left[ \prod\limits_{j=1}^{m} \frac{t^-(j)}{t^+(j)} \right] \sum\limits_{j=0}^{m} \left[\frac{1}{t^+(j)} \prod\limits_{k=1}^{j} \frac{t^+(k)}{t^-(k)}  \right]   \right)
\label{noapprox1}
\end{equation}
Assume the exists a scaling relation between the transition probabilities as a function of the fraction of individuals correct and the absolute number, such that $t^+(j) = N t^+(j/N)$, i.e. individual decision rates remain constant so larger groups update more frequently. In the large $N$ limit the summation above may be written as an integral~\cite{doering},

\begin{equation}
\tau \approx N \int_{0}^{x_{ESC}} \exp\left[N\phi(x)\right] \left[ \int_{0}^{x} \frac{1}{t^+(y)}\exp\left[-N\phi(y)\right] dy \right] dx
\label{approx1}
\end{equation}
where $x_{ESC} = N_{ESC}/N$ and $\phi(x)$ defines the effective potential of the system and is defined as 
\begin{equation}
\phi(x) =  -\int_{0}^{x} \ln\left(\frac{t^+(y)}{t^-(y)}\right) dy
\label{potential}
\end{equation}
The asymptotic behavior of Eqn.~\ref{approx1} in the large $N$ limit may be found by employing Laplace's method for approximating integrals. Following ~\cite{vankampen} we make use of the fact that the integrals are dominated by the behavior of the potential near the extrema. As we know the system is bistable, we refer to the metastable incorrect state as $x_1$, the unstable fixed point as $x_2$, and the metastable correct state as $x_3$, with $x_1<x_2\le N_{ESC}/N < x_3$. The outer integral of Eqn.~\ref{approx1} is therefore approximated as

\begin{equation}
N \int_{0}^{x_{ESC}} \exp\left[N\phi(x)\right] f(x) dx \approx \sqrt{\frac{2\pi N}{\vert \phi''(x_2) \vert}}  \exp\left[N\phi(x_2)\right] f(x_2) 
\label{laplace_out}
\end{equation}
As $x_1<x_2$ this may be repeated for the inner integral to leave
\begin{equation}
\tau \approx  \frac{2\pi \exp\left[N \phi(x_2)-N \phi(x_1) \right] }{t^+(x_1)\sqrt{\vert \phi''(x_2) \vert \phi''(x_1)}}.
\label{laplace_approx}
\end{equation}
Taking logarithms, derivatives, and again assuming large $N$, leaves
\begin{equation}
N^{-1}  \frac{d \ln \tau}{d \sigma} \approx -\int_{x_1}^{x_2} \frac{\partial}{\partial \sigma}\ln\left(\frac{t^+(y)}{t^-(y)}\right) dy
\label{laplace_approx}
\end{equation}

\section{Transition rates}
The dynamics of an update step in stochastic decision process are as follows; first an individual is selected at random from the population, this individual has a personal estimate of the environmental cue $g_i$ and observes the opinions of all its neighbors. The decision rule of Eqn.~\ref{opt_rule} is then employed and the individual will adopt, or remain in, the state most likely to be correct.
For any value of social information $x_L$ there is a value of personal information above which the individual will switch to $S=1$. We denote this value as $g_c$ and from Eqn.~\ref{opt_rule} 
\begin{equation}
g_c(x_L) = \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
\end{equation}
If $g_i>g_c$ then the individual will switch to $S=1$ otherwise $S=-1$. 
Dealing first with the transition rate toward the correct state, we may write this as
\begin{equation}
%t^+(x) = P(S_i=-1)\sum_{j=0}^{N_s}P\left(g_i>g_c(j/N_s)\right)P\left(x_L=j/N_s|x\right)
t^+(x) = P(S_i=-1)\sum_{x_{Li}}P\left(g_i>g_c(x_{Li})\right)P\left(x_{Li}|x\right)
\end{equation}
where $i$ denotes the selected individual and the summation is taken over all possible values of $x_{Li}$.
he product of the probability that the focal individual is in the state $S=-1$ by the probability of a given value of $x_L$ by the

%\bibliographystyle{model1-num-names}
%\bibliographystyle{apalike}
%\bibliography{DvsLA}
\bibliographystyle{apsrev}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{influence}

\end{document}

### 2015-03-18 py_analysis/optimal_sig.py
file for computing value of optimal noise

@@ -1,0 +1,69 @@
+
+#!/usr/bin/python
+
+import sympy as sp
+from IPython.display import display
+import numpy as np
+import matplotlib.pyplot as plt
+import math as m
+import matplotlib as mpl
+from scipy import integrate
+from scipy import optimize
+
+NA = 128
+Ns =800
+K = 90       
+ws = 0.524
+
+def tswup( xx, sig ):
+    gc = np.log(K)*sig*(1.0-2.0*xx)/(2.0)
+    A = np.log(K)/(2.0) - 1/sig
+    B = np.log(K)
+    if gc>1:
+
+        return 0.5*m.exp(-(A-B*xx))
+    else:
+        return 1.0 - 0.5*m.exp((A-B*xx))
+
+def EXTSWUP(X,sig):  
+    return sum(sp.binomial(Ns,j) * X**j* (1-X)**(Ns-j)* tswup(j/float(Ns),sig) for j in xrange(0,Ns+1))
+def tup(X,sig):
+    return (1-X)*(EXTSWUP(X,sig))
+def tdown(X,sig): 
+    return (X)*(1.0-EXTSWUP(X,sig))
+def EXTAPPROX(X,sig):  
+    A = np.log(K)/(2.0) - 1/sig
+    B = np.log(K)
+    VR = 0.5*B**2/float(Ns)
+    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+def EXTAPPROX1(X,sig):  
+    A = np.log(K)/(2.0) - 1/sig
+    B = np.log(K)
+    VR = 0.5*B**2/float(Ns)
+    Y =  (A-m.log(B/2))/B
+ #   Y=A/B
+    return m.exp(-A)*0.5*m.exp((B*Y))*(1.0 +  B*(X-Y)  +  0.5*B**2 * (X-Y)**2)*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+numA = 15
+sigs = np.zeros(numA)
+atimes = np.zeros(numA)
+atimes2 = np.zeros(numA)
+alpha = 0.0
+
+dx = 0.01
[…]

### 2015-03-18 py_analysis/optimal_sig.py
linear approx to x1x2

@@ -36,12 +36,57 @@ def EXTAPPROX(X,sig):
     B = np.log(K)
     VR = 0.5*B**2/float(Ns)
     return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+def EXTAPPROX2(X,sig):  
+    return 2*(2*X-1.0)/(2*X+1.0)
 def EXTAPPROX1(X,sig):  
-    A = np.log(K)/(2.0) - 1/sig
+    A = np.log(K)/(2.0) - 1/float(sig)
     B = np.log(K)
     VR = 0.5*B**2/float(Ns)
+    C = 0.5*B**2/float(Ns)
+    D = C*  (alpha*  (Ns-1) - 1.0)
+
     Y =  (A-m.log(B/2))/B
+#   Y= 0.1#A/B
+#  return m.exp(-A)*0.5*m.exp((B*Y))*(((1.0  - B*Y  +  0.5*B**2 * ( Y**2))  ) + X*(( B  +  0.5*B**2 * (-2*Y )) + (C   - C*B*Y  +  0.5*B**2 *C*( Y**2)) ) + X**2*((  0.5*B**2 ) + ( C*B  +  0.5*B**2 *C*(-2*Y ))  + (1.0   - B*Y  +  0.5*B**2 * (Y**2))*( D )))
+#   return m.exp(-A)*0.5*m.exp((B*Y))*((1.0 +  B*X - B*Y  +  0.5*B**2 * (X**2-2*X*Y + Y**2)) + (C*X+  C*B*X**2 - C*B*Y*X  +  0.5*B**2 *C*X*(X**2-2*X*Y + Y**2))  + (1.0   - B*Y  +  0.5*B**2 * (Y**2))*( D * X**2))
+    return -A + ((B*X))#*(1.0 +  B*(X-Y)  +  0.5*B**2 * (X-Y)**2)*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+    return m.exp(-A)*0.5*m.exp((B*X))#*(1.0 +  B*(X-Y)  +  0.5*B**2 * (X-Y)**2)*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
[…]

### 2015-03-19 py_analysis/optimal_sig.py
working approximation to x2

@@ -11,7 +11,7 @@ from scipy import integrate
 from scipy import optimize
 
 NA = 128
-Ns =800
+Ns =18
 K = 90       
 ws = 0.524
 
@@ -32,7 +32,7 @@ def tup(X,sig):
 def tdown(X,sig): 
     return (X)*(1.0-EXTSWUP(X,sig))
 def EXTAPPROX(X,sig):  
-    A = np.log(K)/(2.0) - 1/sig
+    A = np.log(K)/(2.0) - 1/float(sig)
     B = np.log(K)
     VR = 0.5*B**2/float(Ns)
     return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
@@ -89,11 +89,17 @@ def SOLVEQUAD(sig):
     return m.exp(-A)*0.5*m.exp((B*Y))*((1.0 +  B*X - B*Y  +  0.5*B**2 * (X**2-2*X*Y + Y**2)) + (C*X+  C*B*X**2 - C*B*Y*X  +  0.5*B**2 *C*X*(-2*X*Y + Y**2))  + (1.0   - B*Y  +  0.5*B**2 * (Y**2))*( D * X**2))
     return m.exp(-A)*0.5*m.exp((B*Y))*(1.0 +  B*(X-Y)  +  0.5*B**2 * (X-Y)**2)*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
     return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+def fullX(X,sig):  
+# ax^2 + bx + C = 0
+    A = np.log(K)/(2.0) - 1.0/float(sig)
+    B = np.log(K)
+    return X*(1- ((B**2*X)/(2.0*(B*X-1)))*(alpha*X + (1-X)/Ns ))
+    return (1.0-A)/(2.0-B)
 numA = 15
 sigs = np.zeros(numA)
 atimes = np.zeros(numA)
 atimes2 = np.zeros(numA)
-alpha = 0.0
+alpha = 0.12
 
 dx = 0.01
 xs = np.arange(0,1.0,dx)
@@ -104,13 +110,13 @@ ex = [EXTAPPROX(x,sigma) for x in xs]
[…]

### 2015-03-19 paper/manuscript.tex
start of PRL write-up

--- 2015-03-12 report/report.tex
@@
-\documentclass[3p,number,sort&compress,times]{elsarticle}
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4} 
 \usepackage{amsmath,amsfonts}  %for mathstyles
@@
 \usepackage{graphicx}
-\journal{..}
+%\journal{..}
 %opening
@@
 \begin{document}
-\begin{frontmatter}
+%\begin{frontmatter}
 %\preprint{}
 \title{Optimal strategies of influence in structured populations}
-\author[ex]{Colin J. Torney}
-\author[eeb]{Simon A. Levin}
-%
-%\cortext[cor1]{Corresponding author}
-\address[ex]{Centre for Mathematics \& the Environment, University of Exeter, Penryn Campus, Cornwall, UK}
-\address[eeb]{Department of Ecology \& Evolutionary Biology, Princeton University, Princeton, NJ, USA}
+\author{Colin J. Torney}
+\affiliation{Centre for Mathematics \& the Environment, University of Exeter, Penryn Campus, Cornwall, UK}
+%\affiliation{Department of Ecology \& Evolutionary Biology, Princeton University, \\Princeton, New Jersey 08544}
+\author{Simon A. Levin}
+\affiliation{Department of Ecology \& Evolutionary Biology, Princeton University, \\Princeton, New Jersey 08544}
 
 \begin{abstract}
-Conventions, opinions, or social norms often persist within interacting populations long after their usefulness has ended or their inaccuracy revealed.
-In many scenarios this is due to conformity by individuals, or the devaluation of individual preferences and opinions when they contradict observed social information.
-Both the behavior at the individual-level and the structure of the social network play a role in transitions away from out-dated, collectively-held opinions.
-Personal preferences, biases and the predilection to conform are significant factors, however system level characteristics, such as the statistical properties of the network, or the rate of social mixing, are also strong determinants of macroscale behavior.
-When seeking to influence a collective decision, different strategies may be more or less effective depending on these factors.
-Here we show that the effectiveness of a given strategy of influence is dependent on the nature of the underlying interaction network.
+Incorrect opinions often persist for long periods within interacting populations.
+In many scenarios this is due to conformity and the devaluation of individual opinions when they contradict observed social information.
+Both individual characteristics and system-level properties control the expected time to transition away from an out-dated collective opinion.
+These factors also determine the effectiveness of strategies to engineer transitions to the optimal state.
+By analysing a model of opinion dynamics, we show here how the optimal strategy of influence relates to the underlying interaction network.
 \end{abstract}
-
-\end{frontmatter}
+\maketitle
+%\end{frontmatter}
 
@@
 \end{equation}
-\begin{figure*}
-\centering
-\includegraphics[scale=0.4]{figures/fig-chi.eps} 
-\caption{Probability to transition as a function of local neighbourhood for different values of the sociality weighting $\chi$}
-\label{fig1}
-\end{figure*}
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.4]{figures/fig-chi.eps} 
+%\caption{Probability to transition as a function of local neighbourhood for different values of the sociality weighting $\chi$}
+%\label{fig1}
+%\end{figure*}
 We need to find $\tau$.
-\section{Mean first passage time away from incorrect state}
+%\section{Mean first passage time away from incorrect state}
 Consider the process as a one-step Markov chain on the integer line from $0$ to $N$.
@@
 
-\begin{equation}
-N \int_{0}^{x_{ESC}} \exp\left[N\phi(x)\right] f(x) dx \approx \sqrt{\frac{2\pi N}{\vert \phi''(x_2) \vert}}  \exp\left[N\phi(x_2)\right] f(x_2) 
+\begin{align}
+N \int_{0}^{x_{ESC}} &\exp\left[N\phi(x)\right] f(x) dx    \nonumber \\ 
+ &\approx \sqrt{\frac{2\pi N}{\vert \phi''(x_2) \vert}}  \exp\left[N\phi(x_2)\right] f(x_2) 
 \label{laplace_out}
-\end{equation}
+\end{align}
 As $x_1<x_2$ this may be repeated for the inner integral to leave
@@
 
-\section{Transition rates}
+%\section{Transition rates}
 The dynamics of an update step in stochastic decision process are as follows; first an individual is selected at random from the population, this individual has a personal estimate of the environmental cue $g_i$ and observes the opinions of all its neighbors.

### 2015-03-19 py_analysis/optimal_sig.py
approx for x1

@@ -54,9 +54,11 @@ def EXTAPPROX1(X,sig):
     return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
 def SOLVEQUAD1(sig):  
 # ax^2 + bx + C = 0
-    A = np.log(K)/(2.0) - 1.0/float(sig)
+    A = np.log(K)/(2.0)
+    C =  m.exp(-1.0/float(sig))
+    C =  1.0 -1.0/float(sig)
     B = np.log(K)
-    return 1.0/(2*m.exp(A) - B)
+    return 1.0/(2*m.exp(A)*(C) - B)
     VR = 0.5*B**2/float(Ns)
     C = 0.5*B**2/float(Ns)
     D = C*  (alpha*  (Ns-1) - 1.0)
@@ -111,10 +113,12 @@ ex1 = [EXTAPPROX1(x,sigma) for x in xs]
 ex2 = [EXTAPPROX2(x,sigma) for x in xs]
 #for p in pot: print p
 x2 = SOLVEQUAD(sigma)
+x1 = SOLVEQUAD1(sigma)
 x2 = fullX(x2,sigma)
 plt.plot(xs,ex,linestyle='-')
 #plt.plot(xs,(ex1),linestyle='-')
 plt.plot(x2, x2,'ro')
+plt.plot(x1, x1,'ro')
 plt.plot(xs,xs,linestyle='-')
 plt.axis([0, 0.5, 0, 0.5])
 plt.show()

### 2015-03-20 paper/manuscript.tex
bib file

@@
 P(g_i) = \frac{1}{2\sigma} \exp{ \left( - \frac{\vert g_i - G \vert}{\sigma} \right)}
+\label{lapdist}
 \end{equation}
@@
 \begin{equation}
-N^{-1} \frac{d \ln \tau}{d \sigma} = \beta \sigma^{-2}
+ \frac{d \ln \tau}{d \sigma} = N \beta \sigma^{-2}
 \end{equation}
@@
 \begin{equation}
-N^{-1}  \frac{d \ln \tau}{d \sigma} \approx -\int_{x_1}^{x_2} \frac{\partial}{\partial \sigma}\ln\left(\frac{t^+(y)}{t^-(y)}\right) dy
-\label{laplace_approx}
+  \frac{d \ln \tau}{d \sigma} \approx - N \int_{x_1}^{x_2} \frac{\partial}{\partial \sigma}\ln\left(\frac{t^+(y)}{t^-(y)}\right) dy
+\label{laplace_cost}
 \end{equation}
@@
 \begin{equation}
-g_c(x_L) = \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
+g_c  = \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
 \end{equation}
@@
 %t^+(x) = P(S_i=-1)\sum_{j=0}^{N_s}P\left(g_i>g_c(j/N_s)\right)P\left(x_L=j/N_s|x\right)
-t^+(x) = P(S_i=-1)\sum_{x_{Li}}P\left(g_i>g_c(x_{Li})\right)P\left(x_{Li}|x\right)
+t^+(x) = P(S_i=-1)\sum_{x_{L}}P\left(g_i>g_c \right)P\left(x_{L}|x\right)
+\label{up}
 \end{equation}
-where $i$ denotes the selected individual and the summation is taken over all possible values of $x_{Li}$.
-he product of the probability that the focal individual is in the state $S=-1$ by the probability of a given value of $x_L$ by the
+where $i$ denotes the selected individual and the summation is taken over all possible values of $x_{L}$.
+
+From Eqn.~\ref{lapdist}
+\begin{align}
+P\left(g_i>g_c \right) =
+\frac{1}{2}\exp{\left[1/\sigma - \ln\chi  \left(\frac{1}{2}-x_L\right)\right] }.%&\mbox{if } \\
+%1-\frac{1}{2}\exp{\left[-1/\sigma + \ln\chi  \left(\frac{1}{2}-x_L\right)\right] }&\mbox{if } 
+%\end{cases}
+\end{align}
+(This expression is true if $x_L \le 1/2 - 1/(\sigma\ln\chi)$.
+As we are interested in these probabilities only when $x$ is small we restrict our attention to this scenario.) Given this equation we may write Eqn.~\ref{up} as
+\begin{equation}
+t^+(x) = (1-x)  e^{1/\sigma } \mathcal{F}(x)
+\end{equation}
+where 
+\begin{equation}
+ \mathcal{F}(x) = \frac{1}{2}\sum_{x_{L}}\exp{\left[ - \ln\chi  \left(\frac{1}{2}-x_L\right)\right]}P\left(x_{L}|x\right)
+\end{equation}
+and similarly 
+\begin{equation}
+%t^+(x) = P(S_i=-1)\sum_{j=0}^{N_s}P\left(g_i>g_c(j/N_s)\right)P\left(x_L=j/N_s|x\right)
+t^-(x) =x \left(1-  e^{1/\sigma } \mathcal{F}(x)\right)
+\end{equation}
+Taking the derivative of Eqn.~\ref{laplace_cost} and employing a Maclaurin series expansion leaves
+\begin{equation}
+  \frac{d \ln \tau}{d \sigma} \approx - N \sigma^{-2} \int_{x_1}^{x_2} \left(1 + \sum_{n=1}^{\infty} \left(e^{1/\sigma } \mathcal{F}(y)\right)^n  \right) dy
+\label{laplace_cost2}
+\end{equation}
+The extrema of the potential, $x_1,x_2$, are at the points where $t^+(x)=t^-(x)$, i.e.
+where $x=e^{1/\sigma } \mathcal{F}(x)$.
+Since $e^{1/\sigma } \mathcal{F}(x)<x$ $\forall x \in [x_1,x_2]$ the summation terms in the integrand are all strictly less than $x$, hence
+\begin{equation}
+  \frac{d \ln \tau}{d \sigma} \approx - N \sigma^{-2} \left({x_2}-{x_1}\right) + \mathcal{O}\left( \left(x_2-x_1\right)^2\right)
+\label{laplace_cost2}
+\end{equation}
+%\begin{align}
+%P\left(g_i>g_c \right) =
+%1 - \frac{1}{2}\exp{\left[-1/\sigma + \ln\chi  \left(\frac{1}{2}-x_L\right)\right] }%&\mbox{if } \\
+%%1-\frac{1}{2}\exp{\left[-1/\sigma + \ln\chi  \left(\frac{1}{2}-x_L\right)\right] }&\mbox{if } 
+%%\end{cases}
+%\end{align}
+%otherwise.
 

### 2015-03-20 paper/manuscript.tex
small changes
added one line

@@
   \frac{d \ln \tau}{d \sigma} = N \beta \sigma^{-2}
+  \label{cost1}
 \end{equation}
@@
 \end{equation}
+where $i$ denotes the selected individual and the summation is taken over all possible values of $x_{Li}$.
 where $i$ denotes the selected individual and the summation is taken over all possible values of $x_{L}$.
@@
 \begin{equation}
-  \frac{d \ln \tau}{d \sigma} \approx - N \sigma^{-2} \int_{x_1}^{x_2} \left(1 + \sum_{n=1}^{\infty} \left(e^{1/\sigma } \mathcal{F}(y)\right)^n  \right) dy
+  \frac{d \ln \tau}{d \sigma} \approx N \sigma^{-2} \int_{x_1}^{x_2} \left(1 + \sum_{n=1}^{\infty} \left(e^{1/\sigma } \mathcal{F}(y)\right)^n  \right) dy
 \label{laplace_cost2}
@@
 \begin{equation}
-  \frac{d \ln \tau}{d \sigma} \approx - N \sigma^{-2} \left({x_2}-{x_1}\right) + \mathcal{O}\left( \left(x_2-x_1\right)^2\right)
+  \frac{d \ln \tau}{d \sigma} \approx  N \sigma^{-2} \left({x_2}-{x_1}\right) + \mathcal{O}\left( \left(x_2-x_1\right)^2\right)
 \label{laplace_cost2}
 \end{equation}
+Combining Eqns.~\ref{cost1} and~\ref{laplace_cost2} gives the location of minimal cost as
+\begin{equation}
+  \beta =  \left({x_2}-{x_1}\right) 
+\label{laplace_cost_final}
+\end{equation}
+where in deriving this expression we have neglected terms of $\mathcal{O}(1/N)$ and $\mathcal{O}\left( \left(x_2-x_1\right)^2\right)$
+Optimal strategy is therefore achieved by setting $\sigma$ so that the difference between the two extrema is equal to $\beta$.
 %\begin{align}

### 2015-03-25 paper/manuscript.tex
correlation

@@
   \frac{d \ln \tau}{d \sigma} = N \beta \sigma^{-2}
-  \label{cost1}
+  \label{cost_1}
 \end{equation}
@@
  \mathcal{F}(x) = \frac{1}{2}\sum_{x_{L}}\exp{\left[ - \ln\chi  \left(\frac{1}{2}-x_L\right)\right]}P\left(x_{L}|x\right)
+ \label{social}
 \end{equation}
@@
 \end{equation}
-Combining Eqns.~\ref{cost1} and~\ref{laplace_cost2} gives the location of minimal cost as
+Combining Eqns.~\ref{cost_1} and~\ref{laplace_cost2} gives the location of minimal cost as
 \begin{equation}
@@
 Optimal strategy is therefore achieved by setting $\sigma$ so that the difference between the two extrema is equal to $\beta$.
+
+Numerical calculations of $x_2-x_1$ and the optimal strategy are shown in Fig.~\ref{figx2x1}.
+More intuition into the underlying processes that control the distance between the inflexion points may be attained by performing an expansion of the social information, $\mathcal{F}(x)$, in terms of the moments of the sampling process.
+Taylor expanding the inner term %$\exp{\left[ - \ln\chi  \left(\frac{1}{2}-x_L\right)\right]}$
+of Eqn.~\ref{social} around $x_L=x$ leads to % allows us to replace the summation over all values of $x_L$ with its mean and variance, i.e.
+\begin{equation}
+\mathcal{F}(x) = \frac{1}{2}\exp{\left[ - \ln\chi  \left(\frac{1}{2}-x\right)\right]} \left( 1 + \frac{ \ln(\chi)^2}{2}\mbox{Var}(x_L) \right)
+\end{equation}
+Effectively this equation approximates the process of observing a restricted subset of the population.
+The observations of opinions of neighbors represents an estimate, $x_L$, of the true population average opinion, $x$.
+This random process of observations may be approximated in terms of the mean and variance of the sampling.
+While the underlying network structure is complex and non-Markovian, it may be modelled as correlated binomial, in essence we model the process as sampling with pairwise correlation, when there is transitivity near-neighbors are likely to have copied one another hence opinions will be clustered.
+Following ~\cite{witt2004moody}, the variance of a correlated binomial is
+\begin{equation}
+\mbox{Var}(x_L) = x(1-x)\left( \rho + \frac{1-\rho}{N_s} \right)
+\end{equation}
+where $\rho$ is the pairwise correlation coefficient.
+Assuming the network structure and conformity create a positive correlation of opinions amongst neighbors, then we may define an increased likelihood that neighbor $j$ is in state $S_j=1$, given $S_k=1$, so that
+\begin{equation}
+P(S_j=1|S_k=1) = x(1+\alpha)
+\end{equation}
+where $\alpha$ is determined by the transitivity (probability $k$ is in the neighborhood of $j$) and conformity. This means 
+\begin{equation}
+\rho = \frac{x\alpha}{1-x}
+\end{equation}
+and
+\begin{align}
+\mathcal{F}(x) &= \frac{1}{2}\exp{\left[ -  \ln\chi  \left(\frac{1}{2}-x\right)\right]} \times \nonumber \\ & \left( 1 + \frac{ \ln(\chi)^2}{2}\left(\frac{x(1-x(1+\alpha))}{N_s} +  \alpha x^2  \right)   \right).
+\end{align}
+Solutions to $\mathcal{F}(x)=x$ may be constructed with a perturbation method, with small parameters $\alpha$ and $1/N_s$. We begin with 
+\begin{equation}
+x_1 \sim x^0_1 + \alpha x^1_1 + 1/N_s x^2_1
+\end{equation}
+The zeroth order solution is for the mean field where there is no clustering and no noise in the sampling process, hence
+\begin{align}
+x^0  = \frac{1}{2}\exp{\left[ 1/\sigma -  \ln\chi  \left(\frac{1}{2}-x^0\right)\right]} 
+\end{align}
+For small x
+\begin{equation}
+x^0_1 = \frac{1}{\exp{\left[ 1/\sigma -  \ln\chi  \left(\frac{1}{2}\right)\right]}  - \ln\chi}
+\end{equation}
 %\begin{align}

### 2015-07-15 report/report.tex
updated reports and paper

@@
 \begin{equation}
-\frac{\exp{ \left( - \frac{\vert g_i -  \infty \vert}{\sigma} \right)}}{\exp{ \left( - \frac{\vert g_i + \infty \vert}{\sigma} \right)}} > \chi^{1-2x_L}.
+\frac{\exp{ \left( - \frac{\vert g_i -  \infty \vert}{\sigma} \right)}}{\exp{ \left( - \frac{\vert g_i + \infty \vert}{\sigma} \right)}} > \omega^{1-2x_L}.
 \label{rule}
 \end{equation}
-Here we have denoted the fraction of neighbors an individual observes in the state $S=1$ as $x_L$, used $\pm \infty$ as estimates of the actual value of $G$ (these will cancel), and introduced a social weighting variable $\chi$ which may be interpreted as the belief that a single neighbor is correct rescaled by the neighborhood size.
+Here we have denoted the fraction of neighbors an individual observes in the state $S=1$ as $x_L$, used $\pm \infty$ as estimates of the actual value of $G$ (these will cancel), and introduced a social weighting variable $\omega$ which may be interpreted as the belief that a single neighbor is correct rescaled by the neighborhood size.
 This rescaling means decisions are based on the fraction of neighbors that are correct in the local neighborhood and not the absolute number, ensuring a comparison can be made between social networks with varying average degree.
@@
 \begin{equation}
-g_i >  \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
+g_i >  \sigma\ln\omega  \left(\frac{1}{2}-x_L\right) 
 \label{opt_rule}
@@
 %, i.e.
-$\chi = P(S_j=\mbox{sign}(G))^{\vert \mathcal{N}_i \vert }$  the and denote the fraction of neighbors an individual observes in the state $S=1$ as $x_L$.
+$\omega = P(S_j=\mbox{sign}(G))^{\vert \mathcal{N}_i \vert }$  the and denote the fraction of neighbors an individual observes in the state $S=1$ as $x_L$.
 Then the decision rule for the focal individual is to switch to the state $1$ if
@@
 \includegraphics[scale=0.4]{figures/fig-chi.eps} 
-\caption{Probability to transition as a function of local neighbourhood for different values of the sociality weighting $\chi$}
+\caption{Probability to transition as a function of local neighbourhood for different values of the sociality weighting $\omega$}
 \label{fig1}
@@
 \begin{equation}
-g_c(x_L) = \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
+g_c(x_L) = \sigma\ln\omega  \left(\frac{1}{2}-x_L\right) 
 \end{equation}

### 2015-07-15 py_analysis/potential.py

@@ -20,7 +20,7 @@ from matplotlib import colors
 from numpy import *
 
 fig = plt.figure(figsize=(8, 6)) 
-gs = gridspec.GridSpec(1, 2, width_ratios=[1,1]) 
+gs = gridspec.GridSpec(2, 2, width_ratios=[1,1]) 
 ax0 = plt.subplot(gs[0])
 ax1 = plt.subplot(gs[1])
 
@@ -67,23 +67,26 @@ sigs = np.zeros(numA)
 atimes = np.zeros(numA)
 atimes2 = np.zeros(numA)
 alpha = 0.0
-sigma = 20.0
+sigma = 12.0
 dx = 1/128.0
 ups = [atup(x+dx,sigma) for x in arange(0,1,dx)]
 downs = [atdown(x+dx,sigma) for x in arange(0,1,dx)]
 pot=-np.log(np.divide(ups,downs).astype(float32))
 pot=np.cumsum(pot)
+pot[127]=0.0;
 ax0.plot(arange(0,1,dx),pot ,   color = cls[1],linestyle='-')
-for p in pot: print p
+#for p in pot: print p
 
 
-alpha = 0.22
+alpha = 0.00
+sigma = 50.0
 ups = [atup(x+dx,sigma) for x in arange(0,1,dx)]
 downs = [atdown(x+dx,sigma) for x in arange(0,1,dx)]
 pot=-np.log(np.divide(ups,downs).astype(float32))
 pot=np.cumsum(pot)
-for p in pot: print p
-ax0.plot(arange(0,1,dx),pot ,   color = cls[1],linestyle='-')
+pot[127]=0.0;
+#for p in pot: print p
+ax1.plot(arange(0,1,dx),pot ,   color = cls[1],linestyle='-')
     
         
             #if (j%4==0):
@@ -99,12 +102,12 @@ ax0.plot(arange(0,1,dx),pot ,   color = cls[1],linestyle='-')
 l=ax0.legend(loc=1,     ncol=1, borderaxespad=0.5, prop={'size':12})
 #l.set_title('P', prop={'size':12}) 
 #l.get_title().set_fontproperties({'size':12}) 
-ax0.axis([0.0,1.0, -300, 8])
-ax1.axis([0.0, 1.0, -300, 8])
+ax0.axis([0.0,1.0, -25, 0])
+ax1.axis([0.0, 1.0, -25, 0])
 #ax0.set_yscale('log')
 ax1.get_yaxis().set_visible(False)
-ax0.set_title('small network')
[…]

### 2015-07-15 py_analysis/x1x2.py

@@ -10,77 +10,62 @@ import matplotlib as mpl
 from scipy import integrate
 from scipy import optimize
 
-NA = 64
-Ns =80
-K = 900       
+NA = 128
+Ns =180
+K = 90       
 ws = 0.524
+alpha = 0.0
 
-def detODE(X):
-    return np.array([sp.N(EXTAPPROX(X,sigma)-X)],dtype=float)
 def EXTAPPROX(X,sig):  
-    A = np.log(K)/(2.0) - 1/sig
+    A = np.log(K)/(2.0) - 1/float(sig)
     B = np.log(K)
-    VR = 0.5*B**2*X*(1-X)/float(Ns)
-    return m.exp(-A)*0.5*m.exp((B*X))#*(1.0 +  VR +  ((VR/(1.0+VR))*alpha * B * X * (Ns-1)/float(Ns)))
-def EXTAPPROX2(X,sig):  
-    A = np.log(K)/(2.0) - 1/sig
+    VR = 0.5*B**2/float(Ns)
+    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR*X  +  ((VR)*(alpha*  (Ns-1) - 1.0)) * X**2)
+def X1APPROX(X,sig):  
+    A = np.log(K)/(2.0) - 1/float(sig)
     B = np.log(K)
-    VR = 0.5*B**2*X*(1-X)/float(Ns)
-    return m.exp(-A)*0.5*m.exp((B*X))#*(1.0 +  VR +  ((VR/(1.0+VR))*alpha * B * X * (Ns-1)/float(Ns)))
-def EXTAPPROX3(X,sig):  
-    A = np.log(K)/(2.0) - 1/sig
+    return (1.0+1/float(sig))*(K**-0.5)*0.5*(1.0+B*X)
+    return m.exp(-A)*0.5*(1.0+B*X)
+def mfX1(sig):  
+# ax^2 + bx + C = 0
+    A = np.log(K)/(2.0)
+    C =  m.exp(-1.0/float(sig))
+    C =  1.0 -1.0/float(sig)
     B = np.log(K)
-    VR = 0.5*B**2*X*(1-X)/float(Ns)
[…]

### 2015-07-17 paper/manuscript.tex
updated reports and paper
updated paper

@@
 %\preprint{}
-\title{Optimal strategies of influence in structured populations}
+\title{Optimal strategies of influence in structured social groups}
 \author{Colin J. Torney}
@@
 Each individual, $i$, holds an opinion $S_i \in \{ -1,1\}$ that is observable by others in its local neighborhood and is correct when $S_i = \mbox{sign}(G)$.
-Individuals update their states based on social and personal information and a Bayesian decision rule \cite{nitzan1982optimal,perez2011collective, Perreault, torney2015} is employed.
+Individuals update their states based on social and personal information.
+The two information sources are combined such that individual $i$ will adopt the opinion $S_i = 1$ iff
+\begin{equation}
+\frac{g_i}{\sigma} >  \chi  \left(\frac{1}{2}-x_L\right) 
+\label{opt_rule}
+\end{equation}
+where $x_L$ is the fraction of neighbors with the state $S = 1$ in the local (observable) neighborhood of individual $i$, and $\chi$ is a parameter that determines the weighting individuals give to social information.
+
+While we omit the derivation here the rule defined by Eqn.~\ref{opt_rule} is optimal under certain assumptions\cite{nitzan1982optimal,torney2015}, namely that individuals are aware of the noise in their personal estimate, have a constant level of confidence that neighbors are correct, and assume that the opinions of their neighbors are independent.
+The result of Eqn.~\ref{opt_rule} is that the probability of an individual switching to the state $S_i = 1$ is a sigmoidal function of the fraction of local neighbors in that state, with the steepness of the transition determined by the values of $\chi$ and $\sigma$ (see Fig~\ref{figSwitch} for a plot of this function).
+
+plot of function
+
+show escape time depends on network structure and clustering
+
+escape time can be predicted if rho is known at the minima
+
+optimal strategy of influence if there's a cost for reducing sigma
+
+and a Bayesian decision rule \cite{nitzan1982optimal,perez2011collective, Perreault, torney2015} is employed.
 This means that an individual will switch to the state that is the most likely to be correct, given all available information.
@@
 
-Rearranging Eqn.~\ref{rule} leads to a decision rule such that individual $i$ will adopt the opinion $S_i = 1$ iff
-\begin{equation}
-g_i >  \sigma\ln\chi  \left(\frac{1}{2}-x_L\right) 
-\label{opt_rule}
-\end{equation}
+Rearranging Eqn.~\ref{rule} leads to a decision rule such that
 
@@
 \begin{equation}
-x^0_1 = \frac{1}{\exp{\left[ 1/\sigma -  \ln\chi  \left(\frac{1}{2}\right)\right]}  - \ln\chi}
+x^0_1 = \frac{1}{2\sqrt{\chi}(1-1/\sigma) -  \ln\chi}
 \end{equation}
+For x close to 0.5 we make use of the fact that $\ln(2x) \sim 2(x-\frac{1}{2})$
+\begin{equation}
+x^0_2 = \frac{1+1/\sigma - \ln\chi/2 }{2 -  \ln\chi}
+\end{equation}
+
 %\begin{align}

### 2015-07-17 py_analysis/escape_time.py
all desktop changes

@@ -50,7 +50,7 @@ numA = 15
 sigs = np.zeros(numA)
 atimes = np.zeros(numA)
 atimes2 = np.zeros(numA)
-alpha = 0.279
+alpha = 0.30
 for acount in range(numA):
     
     sigma  = 2.5+0.5*float(acount)

### 2015-07-17 py_analysis/potential.py

@@ -24,8 +24,8 @@ gs = gridspec.GridSpec(1, 2, width_ratios=[1,1])
 ax0 = plt.subplot(gs[0])
 ax1 = plt.subplot(gs[1])
 
-NA = 128
-Ns = 8
+NA = 128*2
+Ns = 50
 K = 50       
 ws = 0.524
 # Set the default color cycle
@@ -57,32 +57,40 @@ def EXTAPPROX(X,sigma):
         return 1.0 - (m.exp(A)*0.5*m.exp((-B*X)))*(1.0 +  VR -  ((VR/(2*m.exp(-(A-B*X))-1.0+VR))*alpha * B * X * (Ns-1)/float(Ns)))
     return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR +  ((VR/(1.0+VR))*alpha * B * X * (Ns-1)/float(Ns)))
 def atup(X,sig):
-    return (1-X)*(EXTSWUP(X,sig))
     return (1-X)*(EXTAPPROX(X,sig))
+def tup(X,sig):
+    return (1-X)*(EXTSWUP(X,sig))
 def atdown(X,sig): 
-    return (X)*(1.0-EXTSWUP(X,sig))
     return (X)*(1.0-EXTAPPROX(X,sig))
+def tdown(X,sig): 
+    return (X)*(1.0-EXTSWUP(X,sig))
 numA = 15
 sigs = np.zeros(numA)
 atimes = np.zeros(numA)
 atimes2 = np.zeros(numA)
 alpha = 0.0
 sigma = 20.0
-dx = 1/128.0
+dx = 1/float(NA)
 ups = [atup(x+dx,sigma) for x in arange(0,1,dx)]
 downs = [atdown(x+dx,sigma) for x in arange(0,1,dx)]
 pot=-np.log(np.divide(ups,downs).astype(float32))
 pot=np.cumsum(pot)
 ax0.plot(arange(0,1,dx),pot ,   color = cls[1],linestyle='-')
-for p in pot: print p
+#for p in pot: print p
 
 
-alpha = 0.22
+alpha = 0.3160
 ups = [atup(x+dx,sigma) for x in arange(0,1,dx)]
 downs = [atdown(x+dx,sigma) for x in arange(0,1,dx)]
 pot=-np.log(np.divide(ups,downs).astype(float32))
 pot=np.cumsum(pot)
 for p in pot: print p
[…]

### 2015-07-17 py_analysis/transition.py

@@ -10,17 +10,14 @@ import matplotlib as mpl
 from scipy import integrate
 from scipy import optimize
 
-NA = 128
-Ns =8
-K = 90       
-ws = 0.524
-
+NA = 64
+Ns = 20
+K = 50       
 def tswup( xx, sig ):
     gc = np.log(K)*sig*(1.0-2.0*xx)/(2.0)
     A = np.log(K)/(2.0) - 1/sig
     B = np.log(K)
     if gc>1:
-
         return 0.5*m.exp(-(A-B*xx))
     else:
         return 1.0 - 0.5*m.exp((A-B*xx))
@@ -31,83 +28,48 @@ def tup(X,sig):
     return (1-X)*(EXTSWUP(X,sig))
 def tdown(X,sig): 
     return (X)*(1.0-EXTSWUP(X,sig))
-def EXTAPPROX(X,sig):  
+def EXTAPPROX(X,sig,a):  
     A = np.log(K)/(2.0) - 1/sig
     B = np.log(K)
     VR = 0.5*B**2*X*(1-X)/float(Ns)
-    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR +  ((VR/(1.0+VR))*alpha * B * X * (Ns-1)/float(Ns)))
-def EXTAPPROX0(X,sig):  
+    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR +  ((VR/(1.0+VR))*a * B * X * (Ns-1)/float(Ns)))
+def EXTAPPROX0(X,sig,a):  
     A = np.log(K)/(2.0)# - 1/sig
     B = np.log(K)
     VR = 0.5*B**2*X*(1-X)/float(Ns)
-    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR +  ((VR/(1.0+VR))*alpha * B * X * (Ns-1)/float(Ns)))
-def atup(X,sig):
+    return m.exp(-A)*0.5*m.exp((B*X))*(1.0 +  VR +  ((VR/(1.0+VR))*a * B * X * (Ns-1)/float(Ns)))
+def atup(X,sig,a):
  #   return (EXTAPPROX(X,sig))
-    return (1-X)*(EXTAPPROX(X,sig))
-def atdown(X,sig): 
-    return (X)*(1.0-EXTAPPROX(X,sig))
-numA = 15
-sigs = np.zeros(numA)
-atimes = np.zeros(numA)
-atimes2 = np.zeros(numA)
-alpha = 0
[…]

### 2015-07-17 simulations/escape_time/main.cpp

@@ -27,8 +27,10 @@
 using namespace std;
 using namespace NGraph;
 void generateNetwork(int* net, int blocks, int N, int edges, float trans, gsl_rng* r);
+void generateNetworkSW(int* net, int blocks, int N, int edges, float trans, gsl_rng* r);
 void printGraph(Graph G);
-float cluster_coeff(Graph A, int N);
+float cluster_coeff1(Graph A, int N);
+float cluster_coeff(int* net, int N, int edges);
 float cluster_coeff_v(Graph G, int v);
 int main() 
 {
@@ -54,7 +56,7 @@ int main()
     int N4 = 0.5 * N2;
     int N_ALL = N * numBlocks;
 
-    int Ns = 8;
+    int Ns = 18;
 
     dim3 threadGrid(N);
     curandState *devRands;
@@ -99,7 +101,8 @@ int main()
         sprintf(fileName, "../output/time-%d.npy", int(2.0*NL));
         for (int G=0;G<sigCount;G++)
         {
-            generateNetwork(h_net, numBlocks, N, Ns, 0.2,r);
+            generateNetworkSW(h_net, numBlocks, N, Ns, 0.5,r);
+
              // generate network
             /*for (int b=0;b<numBlocks;b++)
             {
@@ -109,7 +112,7 @@ int main()
             }*/
             CUDA_CALL(cudaMemcpy (d_net, h_net, (N_ALL*Ns) * sizeof(int), cudaMemcpyHostToDevice));
 
-            float sigma = 2.5 + 0.5 * float(G);
+            float sigma = 2.5 + 0.25 * float(G);
 
 
             for (int b=0;b<numBlocks;b++)
@@ -123,6 +126,7 @@ int main()
 
 
 
+            int NESC = int(N * (0.5- 1.0/(sigma*log(chi))) - 1);
 
             for (int t=0;t<maxTime;t++)
             {
@@ -150,7 +154,7 @@ int main()
                     for (int b=0;b<numBlocks;b++)
                     {
  //                       cout<<"block total : "<<h_blockTotals[b]<<endl;
-                        if (h_blockTotals[b]>0.5*N)
+                        if (h_blockTotals[b]>NESC)
                         {
                             if (h_blockTimes[b]<0)
                                 h_blockTimes[b]=t;
@@ -199,7 +203,158 @@ int main()
     }
     return 0;
 }
+void generateNetworkSW(int* net, int blocks, int N, int edges, float trans, gsl_rng* r)
+{
+
+    float av_cc = 0.0f;
[…]

### 2015-07-17 simulations/potential/main.cpp

@@ -24,7 +24,6 @@ int main()
     float* h_down = new float [N+1];
     int* h_upcount = new int [N+1];
     int* h_net = new int [Ns * N_ALL];
-    cout<<Ns*N_ALL<<endl;
     int* h_states = new int[N_ALL];
     int* h_blockTotals = new int[numBlocks];
     int* h_blockTimes = new int[numBlocks];
@@ -76,15 +75,6 @@ int main()
 
             float cluster = 0.85;
             generateNetworkSW(h_net, numBlocks, N, Ns, cluster,r);
-//           return 0;
-
-            // generate network
-            /*for (int b=0;b<numBlocks;b++)
-            {
-                for (int i=0;i<N;i++)
-                    for (int j=0;j<Ns;j++)
-                        h_net[b*N*Ns + i*Ns + j] = gsl_rng_uniform_int(r,N);
-            }*/
             CUDA_CALL(cudaMemcpy (d_net, h_net, (N_ALL*Ns) * sizeof(int), cudaMemcpyHostToDevice));
 
             float sigma = 5.5 + 0.5 * float(G);
@@ -128,196 +118,6 @@ int main()
     }
     return 0;
 }
-void generateNetworkTri2(int* net, int blocks, int N, int edges, float trans, gsl_rng* r)
-{
-
-    float av_cc = 0.0f;
-    int allEdges[N*(edges+1)], a[2], b[N], c[N];
-    for (int bl=0;bl<blocks;bl++)
-    {
-
-        int Ntri = N;
-        for (int i=0;i<N;i++)
-        {
-            allEdges[i*(edges+1)]=0;
-            b[i] = c[i] = i;
-        }
-
-        while (Ntri>1)
-        {
-            // pick 2 individuals
-            gsl_ran_choose (r, a, 2, c, Ntri, sizeof(int));
-            int ni = b[a[0]];
-            int nj = b[a[1]];
-            allEdges[ni*(edges+1)]++;
-            allEdges[ni*(edges+1) + allEdges[ni*(edges+1)]] = nj;
-            allEdges[nj*(edges+1)]++;
-            allEdges[nj*(edges+1) + allEdges[nj*(edges+1)]] = ni;
-            // now connect j to all i's friends
-            for (int i=0;i<allEdges[ni*(edges+1)];i++)
-            {
-                int nk = allEdges[ni*(edges+1) + i + 1];
-                if (nk==nj) continue;
[…]
